Why aren't significance tests commonly used for linear regression diagnostics?

### 2022-10-10 paper_comparison/paper_comparison/paper_comparison.Rmd
add p-value cp

Subjects recruited from Prolific received a fixed payment for participating in the experiment. However, some subjects will try to maximize their earnings for minimum effort. During the review of submissions, if we found a subject objectively demonstrated clear low-effort throughout the experiment, i.e., failed all attention checks, we rejected the submission. The rejected submissions will be removed immediately, and Prolific will automatically recruit another subject as substitution. Therefore, we only paid for approved submissions and no further data screening procedure needed to be applied on the collected data.

In overall, there were a total of 3200 lineup evaluations made by 160 subjects in both experiment I and experiment II respectively, where 320 lineup evaluations were attention checks and were not used in the following analysis.

@@

>>>>

Subjects recruited from Prolific received a fixed payment for participating in the experiment. However, some subjects will try to maximize their earnings for minimum effort. During the review of submissions, if we found a subject objectively demonstrated clear low-effort throughout the experiment, e.g., failed all attention checks, we rejected the submission. The rejected submissions will be removed immediately, and Prolific will automatically recruit another subject as substitution. Therefore, we only paid for approved submissions and no further data screening procedure needed to be applied on the collected data.

In overall, there were a total of 8860 lineup evaluations made by 443 subjects in experiment I, experiment II and experiment III, where 886 lineup evaluations were attention checks and were not used in the following analysis.

@@

## P-value comparison

Visual inference and conventional hypothesis testing are two distinct statistical procedures. As shown in \ref{fig:p-value-comparison}, the visual test almost always gives higher p-values than the conventional test, suggesting that humans have lower confidence and much higher tolerance of the residual departures than the numerical procedure. In fact, only around 58% of the cases, both tests will agree on the rejection decision given 95% confidence level. And in 41% of the cases, visual test does not reject the null hypothesis but conventional test does. This is an indicator of "false alarm"

```{r eval = FALSE}
vi_survey %>%
  filter(lineup_id <= 576) %>%
  filter(is.na(b) | b != 0) %>%
  mutate(test = p_value > 0.05 & conventional_p_value < 0.05) %>%
  {mean(.$test)}
```

```{r p-value-comparison, fig.cap="..."}
vi_survey %>%
  filter(lineup_id <= 576) %>%
  filter(is.na(b) | b != 0) %>%
  group_by(unique_lineup_id) %>%
  summarise(across(everything(), first)) %>%
  # filter(x_dist == "uniform") %>%
  ggplot() +
  geom_point(aes(p_value, conventional_p_value), alpha = 0.4) +
  geom_abline() +
  scale_x_log10() +
  scale_y_log10() +
  facet_wrap(~type)
```

### 2022-10-10 paper_comparison/paper_comparison/paper_comparison.tex
add p-value cp

@@

\begin{center}\includegraphics[width=1\linewidth]{paper_comparison_files/figure-latex/unnamed-chunk-6-1} \end{center}

>>>>

\hypertarget{p-value-comparison}{%
\subsection{P-value comparison}\label{p-value-comparison}}

Visual inference and conventional hypothesis testing are two distinct
statistical procedures. As shown in \ref{fig:p-value-comparison}, the
visual test almost always gives higher p-values than the conventional
test, suggesting that humans have lower confidence and much higher
tolerance of the residual departures than the numerical procedure. In
fact, only around 58\% of the cases, both tests will agree on the
rejection decision given 95\% confidence level. And in 41\% of the
cases, visual test does not reject the null hypothesis but conventional
test does. This is an indicator of ``false alarm''

{\centering \includegraphics[width=1\linewidth]{paper_comparison_files/figure-latex/p-value-comparison-1}

\caption{...}\label{fig:p-value-comparison}
\end{figure}

@@

\begin{center}\includegraphics[width=1\linewidth]{paper_comparison_files/figure-latex/unnamed-chunk-7-1} \end{center}
